---
title: "CLT_WUP"
author: "Dorothy Decker"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k2),' sd = ',sd(my1000$k2)))

```

```{r}
numb = 4
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```



```{r}
numb = 9
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k3 = x.avg


p <- ggplot(my1000, aes(x=k3),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k3)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k3),' sd = ',sd(my1000$k3)))

```

Take the standard deviation and put it in the data that is from the central limit. The standard deviation shrinks as the number gets higher example 4 is divided by 2, 9 is divided by 3. 16 is divided by 4, and so on. The standard deviation is with n=9, 'r not '. The expected value is a lower standard deviation. The mean will always stay the same and the standard deviation will continue to shrink. This is an example of that. The original SD was 41.9769368490273, and the mean was 49.594. The current SD is 14.056796190328, and the mean is 49.895.

We expect 14 and we get `r sd(my1000$k3)`.

```{r}
numb = 16
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k4 = x.avg


p <- ggplot(my1000, aes(x=k4),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k4)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4),' sd = ',sd(my1000$k4)))

```


The standard deviation is now a quarter of what it was before, which is now 10.2194198080463. The mean is still around 49.949875. 
I expected the SD to be smaller than 10, but it was `r sd(my1000$k4)`.


```{r}
numb = 25
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k5 = x.avg


p <- ggplot(my1000, aes(x=k5),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k5)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 25") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k5),' sd = ',sd(my1000$k5)))

```


In numb 25 I am noticing the SD is decreasing, but not as much as before. The new SD is 8.33994705960157, with the mean still being around 49.8944.
We expect 8 and it was `r sd(my1000$k5)`. 


```{r}
numb = 36
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k6 = x.avg


p <- ggplot(my1000, aes(x=k6),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k6)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 36") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k6),' sd = ',sd(my1000$k6)))

```


The SD continues to shrink and the mean still stays the same. The mean is around 49.8716944444444, with the new SD being 6.98431983091458.
We expect 6 and we got `r sd(my1000$k6)` My expected value was off by a little, it rounds up to 7 with the code.
